Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-09-04 paper/ms.tex
add log10sma_vs_log10msini_detectable_check
minor updates

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{August 6, 2020}
\revised{---}
\accepted{---}
\submitjournal{AAS journals.}
\shorttitle{TOI~837 in IC~2602}

@@

\added{The authors thank K.~Anderson for fruitful discussions, and are
grateful to the anonymous referee for their constructive comments and
suggestions.}
%
L.G.B. and J.H. acknowledge support by the TESS GI Program, program
G011103, through NASA grant 80NSSC19K0386.
%
This study was based in part on observations at Cerro Tololo
Inter-American Observatory at NSF’s NOIRLab (NOIRLab Prop. ID
2020A-0146; PI: L{.}~Bouma), which is managed by the Association of
Universities for Research in Astronomy (AURA) under a cooperative
agreement with the National Science Foundation.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.  \tn\ was included on the TESS 2-minute target list in
part thanks to the Guest Investigator program of G.\ Sacco (G011265).
%

>>>>

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{August 6, 2020}
\revised{September 7, 2020}
\accepted{---}
\submitjournal{AAS journals.}
\shorttitle{TOI~837 in IC~2602}

@@

\added{The authors thank K.~Anderson for fruitful discussions, and
T.~Guillot for contributions to the ASTEP project.  We are also
grateful to the anonymous referee for their constructive comments and
suggestions.}
%
L.G.B. and J.H. acknowledge support by the TESS GI Program, program
G011103, through NASA grant 80NSSC19K0386.
%
This study was based in part on observations at Cerro Tololo
Inter-American Observatory at NSF’s NOIRLab (NOIRLab Prop. ID
2020A-0146; PI: L{.}~Bouma), which is managed by the Association of
Universities for Research in Astronomy (AURA) under a cooperative
agreement with the National Science Foundation.
%
This paper includes data collected by the TESS mission, which are
publicly available from the Mikulski Archive for Space Telescopes
(MAST).
%
Funding for the TESS mission is provided by NASA's Science Mission
directorate.  \tn\ was included on the TESS 2-minute target list in
part thanks to the Guest Investigator program of G.\ Sacco (G011265).
%
